\chapter*{Abstract}
Recently, digital libraries (\gls{digilib}) have become a mainstay for students looking for assignments or thesis references. The main problem is that the interface and application flow are often unintuitive and unfriendly, which ultimately makes students reluctant and prefer to look for references elsewhere. Starting from this concern, this research evaluates the \gls{ux} on the \gls{digilib} IIB Darmajaya platform. The main idea is to use the \gls{ueq} method to measure overall user satisfaction. What makes it different, this method directly dissects user impressions from six aspects at once: attractiveness, perspicuity, efficiency, dependability, stimulation, and novelty. After the questionnaire data from the respondents was processed, it became clear which parts of the \gls{digilib} were already performing well and which were still confusing to the users. It is hoped that the results of this evaluation can serve as a concrete guide for the campus IT team to revamp the system interface so that it is more comfortable and pleasant for students to use.

\noindent\textbf{Keywords:} User Experience, UEQ, Digital Library, Digilib Darmajaya, Interface Evaluation.

\chapter*{Abstrak}
Belakangan ini, perpustakaan digital (\gls{digilib}) menjadi andalan mahasiswa untuk mencari referensi tugas atau skripsi. Masalah utamanya, seringkali tampilan dan alur aplikasi kurang intuitif dan bersahabat, yang pada akhirnya bikin mahasiswa malas dan lebih memilih cari referensi di tempat lain. Berangkat dari keresahan tersebut, penelitian ini mengevaluasi pengalaman pengguna (\gls{ux}) pada platform \gls{digilib} IIB Darmajaya. Ide utamanya adalah menggunakan metode \gls{ueq} untuk mengukur kepuasan pengguna secara menyeluruh. Yang bikin beda, metode ini langsung membedah kesan pengguna dari enam sisi sekaligus: daya tarik, kejelasan, efisiensi, ketepatan, stimulasi, dan kebaruan. Setelah data kuesioner dari responden diolah, terlihat jelas bagian mana dari \gls{digilib} yang sudah bagus dan mana yang masih membingungkan pengguna. Harapannya, hasil evaluasi ini bisa jadi panduan konkret bagi tim IT kampus untuk merombak antarmuka sistem agar lebih nyaman dan bikin mahasiswa betah menggunakannya.

\noindent\textbf{Kata kunci:} Pengalaman Pengguna, UEQ, Perpustakaan Digital, Digilib Darmajaya, Evaluasi Antarmuka.